
\bibliographystyle{alpha}
\begin{thebibliography}{Dum74}

  \bibitem[Dis13]{Dis13}
  Filippo Disanto.
  \newblock Andr\'{e} permutations, right-to-left and left-to-right minima.
  \newblock {\em S\'{e}m. Lothar. Combin.}, 70:Art. B70f, 13, 2013.
  
  \bibitem[Dum74]{Dum74}
  Dominique Dumont.
  \newblock Interpr\'{e}tations combinatoires des nombres de {G}enocchi.
  \newblock {\em Duke Math. J.}, 41:305--318, 1974.
  
  \bibitem[FH16]{FH16}
  Dominique Foata and Guo-Niu Han.
  \newblock Andr\'{e} permutation calculus: a twin {S}eidel matrix sequence.
  \newblock {\em S\'{e}m. Lothar. Combin.}, 73:Art. B73e, 54, [2014-2016].
  
  \bibitem[FS73]{FSch73}
  D.~Foata and M.-P. Sch\"{u}tzenberger.
  \newblock Nombres d'{E}uler et permutations alternantes.
  \newblock In {\em A Survey of Combinatorial Theory ({P}roc. {I}nternat.
    {S}ympos., {C}olorado {S}tate {U}niv., {F}ort {C}ollins, {C}olo., 1971)},
    pages 173--187, 1973.
  
  \bibitem[Ful97]{Ful97}
  William Fulton.
  \newblock {\em Young {T}ableaux}, volume~35 of {\em London Mathematical Society
    Student Texts}.
  \newblock Cambridge University Press, Cambridge, 1997.
  \newblock With applications to representation theory and geometry.
  
  \bibitem[IZ22]{IZ22}
  Mee~Seong Im and Jieru Zhu.
  \newblock {Transitioning between tableaux and spider bases for Specht modules}.
  \newblock {\em {Algebras and Representation Theory}}, 25(2):387--399, 2022.
  
  \bibitem[KR84]{KR84}
  Joseph P.~S. Kung and Gian-Carlo Rota.
  \newblock The invariant theory of binary forms.
  \newblock {\em Bull. Amer. Math. Soc. (N.S.)}, 10(1):27--85, 1984.
  
  \bibitem[Kup96]{Kup96}
  Greg Kuperberg.
  \newblock Spiders for rank {$2$} {L}ie algebras.
  \newblock {\em Comm. Math. Phys.}, 180(1):109--151, 1996.
  
  \bibitem[LW20]{LW20}
  Alexander Lazar and Michelle~L. Wachs.
  \newblock On the homogenized {L}inial arrangement: intersection lattice and
    {G}enocchi numbers.
  \newblock {\em S\'{e}m. Lothar. Combin.}, 82B:Art. 93, 12, 2020.
  
  \bibitem[Nak20]{Nak20}
  Tomoki Nakamigawa.
  \newblock The expansion of a chord diagram and the {G}enocchi numbers.
  \newblock {\em Ars Math. Contemp.}, 18(2):381--391, 2020.
  
  \bibitem[PPR09]{PPR09}
  T.~Kyle Petersen, Pavlo Pylyavskyy, and Brendon Rhoades.
  \newblock Promotion and cyclic sieving via webs.
  \newblock {\em J. Algebraic Combin.}, 30(1):19--41, 2009.
  
  \bibitem[Rho19]{Rho19}
  Brendon Rhoades.
  \newblock The polytabloid basis expands positively into the web basis.
  \newblock {\em Forum Math. Sigma}, 7:Paper No. e26, 8, 2019.
  
  \bibitem[RT19]{RT19}
  Heather~M. Russell and Julianna~S. Tymoczko.
  \newblock The transition matrix between the {S}pecht and web bases is unipotent
    with additional vanishing entries.
  \newblock {\em Int. Math. Res. Not. IMRN}, (5):1479--1502, 2019.
  
  \bibitem[Sag01]{Sag01}
  Bruce~E. Sagan.
  \newblock {\em The Symmetric Group}, volume 203 of {\em Graduate Texts in
    Mathematics}.
  \newblock Springer-Verlag, New York, second edition, 2001.
  \newblock Representations, combinatorial algorithms, and symmetric functions.
  
  \bibitem[Sei77]{Sei77}
  Ludwig Seidel.
  \newblock {{\"U}ber eine einfache Entstehungsweise der Bernoulli'schen Zahlen
    u. einiger verwandten Reihen}.
  \newblock 1877.
  
  \bibitem[SI20]{OEIS}
  Neil J.~A. Sloane and The OEIS~Foundation Inc.
  \newblock The on-line encyclopedia of integer sequences, 2020.
  
  \bibitem[Sta94]{Sta94}
  Richard~P. Stanley.
  \newblock Flag {$f$}-vectors and the {$cd$}-index.
  \newblock {\em Math. Z.}, 216(3):483--499, 1994.
  
  \bibitem[Sta99]{Sta99}
  Richard~P. Stanley.
  \newblock {\em Enumerative Combinatorics. {V}ol. 2}, volume~62 of {\em
    Cambridge Studies in Advanced Mathematics}.
  \newblock Cambridge University Press, Cambridge, 1999.
  \newblock With a foreword by Gian-Carlo Rota and appendix 1 by Sergey Fomin.
  
  \bibitem[Sta10]{Sta10}
  Richard~P. Stanley.
  \newblock A survey of alternating permutations.
  \newblock In {\em Combinatorics and graphs}, volume 531 of {\em Contemp.
    Math.}, pages 165--196. Amer. Math. Soc., Providence, RI, 2010.
  
  \bibitem[Sta12]{Sta12}
  Richard~P. Stanley.
  \newblock {\em Enumerative Combinatorics. {V}olume 1}, volume~49 of {\em
    Cambridge Studies in Advanced Mathematics}.
  \newblock Cambridge University Press, Cambridge, second edition, 2012.
  
\end{thebibliography}